\sout{A smart street lighting system based on \rev{an} IPv6-enabled wireless sensor network} \rev{A routing protocol for an urban IoT based on a smart street lighting wireless sensor network}

### 2014-12-19 2014_ELSEVIER_CEE_SI/paper_cee_special_issue.tex
adição de compilação condicional (coluna simples ou dupla)
ajuste no título

%\documentclass[final,authoryear,3p,twocolumn]{elsarticle}

%% Use the option review to obtain double line spacing
\documentclass[authoryear,preprint,review,12pt]{elsarticle}

@@

\title{\sout{A smart street lighting system based on \rev{an} IPv6-enabled wireless sensor network} \rev{A routing protocol for an urban IoT based on a smart streetlighting wireless sensor network}}

@@

\begin{figure}[h!tb]
\centering
\includegraphics[width=0.8\textwidth]{figures/RPL_DIO}
%\includegraphics[width=0.45\textwidth]{figures/RPL_DIO}
\caption{Example of a Destination Oriented Directed Acyclic Graph(DODAG).}
\label{RPL_DIO}
\end{figure}

@@

\begin{figure}[h!tb]
\centering
\includegraphics[width=1\textwidth]{figures/RPL_DAO}
%\includegraphics[width=0.45\textwidth]{figures/RPL_DAO}
\caption{P2P communication between routers $B$ and $C$ through a DODAG root using RPL.}
\label{RPL_DAO}
\end{figure}

@@

%For RPL rank computation, it was used the Objective Function 0 as defined in RFC6552.
\begin{figure}
\centering
\includegraphics[width=1\textwidth]{figures/sample_scenarios.eps}
%\includegraphics[width=0.45\textwidth]{figures/sample_scenarios.eps}
\caption{Sample of simulated scenarios with nodes populated.}
\label{sim_scenarios}
\end{figure}

\begin{figure}
\centering
\includegraphics[width=1\textwidth]{figures/hops_range.eps}
%\includegraphics[width=0.45\textwidth]{figures/final_result.eps}
\caption{Simulation results of the average route length for the routing algorithms (RPL, GOAFR, \textit{GeoRank}, and Dijkstra' algorithm for shortest path).}
\label{sim_results}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=1\textwidth]{figures/mem_usage_range.eps}
%\includegraphics[width=0.45\textwidth]{figures/final_result.eps}
\caption{Simulation results of the size of the routing table in number of entries relative to the number of nodes in the network, for the routing algorithms RPL and \textit{GeoRank}}
\label{sim_results2}
\end{figure}

>>>>

%\newcommand*{\TWOCOL}{}% define 2 cols option

\ifdefined\TWOCOL
\documentclass[final,authoryear,3p,twocolumn]{elsarticle}
%% Use the option review to obtain double line spacing
\else
\documentclass[authoryear,preprint,review,12pt]{elsarticle}
\fi

@@

\title{\sout{A smart street lighting system based on \rev{an} IPv6-enabled wireless sensor network} \rev{A routing protocol for an urban IoT based on a smart street lighting wireless sensor network}}

@@

\begin{figure}[h!tb]
\centering
\ifdefined\TWOCOL
\includegraphics[width=0.45\textwidth]{figures/RPL_DIO}
\else
\includegraphics[width=0.8\textwidth]{figures/RPL_DIO}
\fi
\caption{Example of a Destination Oriented Directed Acyclic Graph(DODAG).}
\label{RPL_DIO}
\end{figure}

@@

\begin{figure}[h!tb]
\centering
\ifdefined\TWOCOL
\includegraphics[width=0.45\textwidth]{figures/RPL_DAO}
\else
\includegraphics[width=1\textwidth]{figures/RPL_DAO}
\fi
\caption{P2P communication between routers $B$ and $C$ through a DODAG root using RPL.}
\label{RPL_DAO}
\end{figure}

@@

%For RPL rank computation, it was used the Objective Function 0 as defined in RFC6552.
\begin{figure}
\centering
\ifdefined\TWOCOL
\includegraphics[width=0.45\textwidth]{figures/sample_scenarios.eps}
\else
\includegraphics[width=1\textwidth]{figures/sample_scenarios.eps}
\fi
\caption{Sample of simulated scenarios with nodes populated.}
\label{sim_scenarios}
\end{figure}

\begin{figure}
\centering
\ifdefined\TWOCOL
\includegraphics[width=0.45\textwidth]{figures/hops_range.eps}
\else
\includegraphics[width=1\textwidth]{figures/hops_range.eps}
\fi
\caption{Simulation results of the average route length for the routing algorithms (RPL, GOAFR, \textit{GeoRank}, and Dijkstra' algorithm for shortest path).}
\label{sim_results}
\end{figure}

@@

\begin{figure}
\centering
\ifdefined\TWOCOL
\includegraphics[width=0.45\textwidth]{figures/mem_usage_range.eps}
\else
\includegraphics[width=1\textwidth]{figures/mem_usage_range.eps}
\fi
\caption{Simulation results of the size of the routing table in number of entries relative to the number of nodes in the network, for the routing algorithms RPL and \textit{GeoRank}}
\label{sim_results2}
\end{figure}
